From Predicate Automata to Alternating Data Automata

### 2017-05-17 predicate-automata.tex
ok

\include{commands}

@@

Let $Q$ be a finite set of predicates, where for each $q \in Q$, we
denote by $\#(q)\geq0$ its arity. We denote by $Q_0$ the subset of $Q$
consisting of predicates of arity zero. By $\Sigma$ we denote a
finite set of symbols, called alphabet.

We consider an infinite countable set $\vars$ of first-order
variables, ranging over $\nat$, and we associate each predicate $q \in
Q$ a tuple of arguments $\vec{x}_q = \tuple{x_{q,1}, \ldots,
  x_{q,\#(q)}}$ such that, for any two $p,q \in Q$, $\vec{x}_p$ and
$\vec{x}_q$ have no elements in common, when $p \neq q$.

>>>>

\include{commands-lncs}

@@

Let $Q$ be a finite set of predicates, where for each $q \in Q$, we
denote by $\#(q)\geq0$ its arity. We denote by $Q_0$ the subset of $Q$
consisting of predicates of arity zero. By $\Sigma$ we denote a finite
set of symbols, disjoint from $Q$, called an alphabet.

We consider an infinite countable set $\vars$ of first-order
variables, ranging over $\nat$. For a tuple of variables $\vec{x} =
\tuple{x_1,\ldots,x_n}$, we define a one-to-one corresponding tuple
$\overline{\vec{x}} = \tuple{\overline{x_1},\ldots,\vec{x_n}}$. We
associate each predicate $q \in Q$ a tuple of arguments $\vec{x}_q =
\tuple{x_{q,1}, \ldots, x_{q,\#(q)}}$ such that, for any two $p,q \in
Q$, if $p \neq q$ then any two of $\vec{x}_p$, $\overline{\vec{x}}_p$,
$\vec{x}_q$ and $\overline{\vec{x}}_q$ have no elements in common,
respectively.

An \emph{atom} is a predicate $q(\vec{x}_q)$,
$q(\overline{\vec{x}}_q)$, $x \teq y$ or $x \not\teq y$, for $x,y \in
\vars$ and a \emph{formula} is a positive boolean combination of
atoms. We denote by $\Form(Q,\vec{x})$ the set of formulae with
predicates from $Q$ and variables from $\vec{x}$.

\begin{definition}[Predicate Automata]
\end{definition}
